### 2013-11-24 tests_Auto-Mpg.Rmd
added non red data (Auto-MPG & Kinetics)
Auto-MPG does not have practically any diif
Kinetics non-reg is a little bit *better* :-(

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50, lambda=0.8)

@@

save(report, file="Auto-Mpg300.Rda") # recover with load("Auto-Mpg300.Rda")

@@

write.table(df, "Auto-Mpg300.txt")

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, lambda=1, runs=25)

@@

save(report, file="Auto-Mpg300_lambda1.Rda") # recover with load("Auto-Mpg300.Rda")

@@

write.table(df, "Auto-Mpg300_lambda1.txt")

### 2013-11-24 tests_Kinematics.Rmd
added all data results on latex file
added non red data (Auto-MPG & Kinetics)
Auto-MPG does not have practically any diif
Kinetics non-reg is a little bit *better* :-(

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, runs=25, lambda=0.8)

@@

save(report, file="Kinematics300_lambda0.8_25runs.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "Kinematics200.txt")

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, runs=25, lambda=1)

@@

save(report, file="Kinematics300_lambda1.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "Kinematics300_lambda1.txt")
